\huge A Usability Evaluation of Tor Launcher

### 2016-10-24 pets2017-paper/pets2017-paper.tex
word fixes.

We concluded with a summative usability test~\cite{summative} that determined the usability of an interface. We test the current interface to evaluate it. Opportunistically, we also test the redesigned interface as well. Summative usability testing is a quality assurance tool designed to test features in a design. In short, formative testing tells you {\it what} is or is not usable, while summative testing testing tells you {\it if} it is or is not usable. 20 users is considered to be the minimum number to statistically significant measurments~\cite{howmanyusers}, so we recruited for 20 participants in each experimental condition.

@@

We first examined tasks required, inputs taken, and consequences of possible actions on each screeen to map all potential paths through the interface (Figure~\ref{fig:digraph}). We then stepped through each user path, systematically toggling all actions and inputs.

>>>>

We concluded with a summative usability test~\cite{summative} that determined the usability of an interface. We test the current interface to evaluate it. We also opportunistically test the redesigned interface. Summative usability testing is a quality assurance tool designed to test features in a design. In short, formative testing tells you {\it what} is or is not usable, while summative testing testing tells you {\it if} it is or is not usable. 20 users is considered to be the minimum number to statistically significant measurments~\cite{howmanyusers}, so we recruited for 20 participants in each experimental condition.

@@

We first examined each screen in the interface for tasks required, inputs taken, and consequences of possible actions. This was done to map all potential paths through the interface (Figure~\ref{fig:digraph}). We then stepped through each user path and recorded our observations.
